% Abstract for the TUM report document
% Included by MAIN.TEX

\begin{center}
{\Large \textbf Acknowledgement}
\end{center}
\vspace{1cm}

I would like to take this opportunity and express my biggest gratitude to everyone, who supported me through all the ups and downs I had during my time at the Univesity of Kaiserslautern. 

Firstly, I am very grateful to \textbf{Prof. Dr. Arnd Poetzsch-Heffter} and my thesis supervisor \textbf{Dr. rer. nat. Annette Bieniusa} for making it possible for me to work on the topic that suits my area of interest. Moreover, I want to thank Annette for having the door to her office always open for a discussion, whenever I needed it. I am happy I had a chance to work with her on multiple occasions: firstly, during the time of the lecture on Compiler and Language-Processing Tools; then, while being a research assistant in EU Project "Lightkone"; and, finally, by writing a Master's thesis under her guidance. She was always patient and continuously motivated me to strive for better results. I could not ask for more.

Next, I would like to thank the stuff at Software Technology Group, who made me feel very welcome and patiently answered any questions I had. Especially, \textbf{Mathias Weber}, \textbf{Peter Zeller}, and \textbf{Deepthi Akkoorath}.

Finally, I want to mention my friends, family and, particularly, \textbf{my parents} and \textbf{sister}. They did their very best to encourage and motivate me throughout the whole period of my study in Germany. Nothing of it would ever be possible without them. Thank you.